%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.40\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Udeep}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Shrestha}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Full Stack Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.3\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Kathmandu, Nepal}\\
	\icon{Phone}{12}{+977 9849324652}\\
	\icon{At}{12}{\href{mailto:udeepbahadur7@gmail.com}{udeepbahadur7@gmail.com}}\\	
\end{minipage}
\begin{minipage}[t]{0.3\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Github}{12}{\href{https://github.com/udeepbahadur7}{github.com/udeepbahadur7}}\\
	\icon{Twitter}{12}{\href{https://twitter.com/@ShresthaUdeep}{@ShresthaUdeep}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	I'm a people person and dependable team player. I'm the kind of person who knows how to execute tasks with precision. I pay attention to all the details of a project so that project is completed in time. 
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{JavaScript}{80}
		\baritem{ExpressJS}{80}
		\baritem{PostgresSQL}{80}
		\baritem{AWS Services}{70}
		\baritem{Python}{80}
		\baritem{Docker}{70}
		\baritem{Nginx}{70}
		\baritem{CSS}{60}
		\baritem{Django}{80}
		\baritem{React}{80}
	\end{barchart}
\end{minipage}

\begin{center}
	\bubbles{6/PyCharm, 6/Webstorm, 6/git, 6/VS Code, 6/Vim}
\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
\entry
		{Nov 2017 -- May 2018}
		{Full Stack Developer}
		{www.infiniabiz.com}
    		{
    InfiniaBiz is a business productivity tool, enabling companies to increase sales, revenue and profits. Companies can send purchase RFQs to vendors and vendors can reply to those RFQs.\\ 
    		    \texttt{React}\slashsep\textt{Redux}\slashsep\texttt{Django}\slashsep\texttt{CSS}\slashsep\textt{Docker}\slashsep\textt{Nginx}\slashsep\textt{Digital Ocean}}
	\entry
		{May 2018 -- Aug 2018\\\footnotesize{}}
		{Django Developer}
		{www.infiniasmart.com}
		{
		    InfiniaSmart is a Wifi-marketing application. Customers logging into the wifi in hotels, restaurants are shown their promotional items before logging in. Restaurant owner can view their wifi usage, customer details and also send sms on special occasion\\
		    \texttt{Vue.js}\slashsep\texttt{Node.js}\slashsep\texttt{Express JS}\slashsep\textt{Docker}\slashsep\textt{Nginx}\slashsep\textt{Digital Ocean}
		}
	\entry
		{July 2018 -- Aug 2018\\\footnotesize{}}
		{Laravel Developer}
		{}
		{
		   A freelance project I had completed for Australian University. I had to build admin panel and forms in Laravel\\ \texttt{PHP}\slashsep\texttt{Laravel}
		}
	\entry
	    {Sept 2018 -- March 2018}
	    {Full Stack Developer}
	    {}
	    {
	        Inventory Management System where organization can track their stocks, sales and purchases.\\
	        \texttt{Django}\slashsep\textt{Django Rest Framework}\slashsep\textt{React\slashsep\textt{Redux}}\slashsep\textt{Redux Saga}\slashsep\textt{AWS EC2, S3}
	    }
	    
	 \entry{May 2019 -- Sept 2019}{Node Developer}{}
	    {Seat reserving and payment system using seats.io and stripe API\\
	        \texttt{Express}\slashsep\textt{EJS templating}\slashsep\textt{Seats.io API}\slashsep\textt{Stripe API}
	    }
	    
	  \entry
		 {Nov 2018 -- May 2019}
		{Senior Full Stack Developer}
		{jhilkoinc.com}
		{
		During this period, my responsibilities were choosing right software stack for the vehicle tracking system, mentoring the team members in learning the software stack, planning and executing the sprints, reporting weekly progress to CEO and developing dev-tools to help improve team’s productivity. I worked on ReactJs and react-native to build web applications and mobile applications using Javascript.

		
		\\ \texttt{Express}\slashsep\texttt{React}\slashsep\texttt{Bootstrap}\slashsep\texttt{React Native}\slashsep\texttt{MongoDB}\slashsep\texttt{MongoDB}\slashsep\texttt{Socket.io}\slashsep\texttt{GitLab}}
		
		
	  \entry
		 {July 02, 2019 -- present}
		{Senior Full Stack Developer}
		{services.khalti.com}
		{
		During this period, my role was consuming new Service APIs in different forms like REST and SOAP from different vendors, distributing APIs among the team,  migrating existing AngularJS applications to React and optimizing the database queries.
		
		\\ \texttt{Django}\slashsep\texttt{Python}\slashsep\texttt{React Hooks}\slashsep\texttt{Material UI}\slashsep\texttt{Docker}\slashsep\texttt{Nginx}\slashsep\texttt{Postgres}\slashsep\texttt{AWS}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2012-2016}
		{Bachelor's Degree}
		{Pulchowk Campus, Pulchowk, Kathmandu}
		{Computer Engineering}
	\entry
		{2009 -- 2011}
		{+2}
		{St. Xavier's College, Maitighar, Kathmandu}
		{physics, chemistry, maths, biology}
	\entry
		{2009}
		{School Leaving Certificate}
		{Naulo Jyoti English School, Thimi, Bhaktapur}
		{\lorem\lorem}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{Nepali} - native\\
	\textbf{English} - proficient\\
	\textbf{Newari} - proficient\\
	\textbf{Hindi} -rudimentary
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	
	I love playing football, travelling and exploring new programming concepts.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Interests}
	
	Big Data, Machine Learning and AWS Services. Currenly learning \textbf{React Native} and \textbf{Flutter} during free time.
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
